The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2025-02-21 index.qmd
added github and binder link

number-sections: false
citation:
  container-title: Pediatric Research
  volume: 97
  issue: 2
  doi: "not yet assigned"
# date: last-modified
bibliography: Gavin_Thesis_Ref.bib
csl: nature.csl

>>>>

number-sections: false
citation:
  container-title: Pediatric Research
  volume: 97
  issue: 2
  doi: "not yet assigned"
date: last-modified
bibliography: Gavin_Thesis_Ref.bib
csl: nature.csl
